### 2021-08-12 paper/paper.tex
frontend/backend -> front end/back end (seems to be the most used form)

Such a difference between the programming languages used in the front- and
backend leads to a well-known barrier between a user and the developers of a library.
Julia was designed from the beginning to make it possible to write both simple
high-level code and highly efficient compute kernels, thereby solving the
two-language problem --- at least to a significant extent. Highly efficient low-level
code will still look different from simple high-level code, but the
barrier between them is much smaller. In particular, this makes it easier for
users to transition to developers and contribute to a package. This also contributes
to the following observation:

>>>>

Such a difference between the programming languages used in the front end and
back end leads to a well-known barrier between a user and the developers of a library.
Julia was designed from the beginning to make it possible to write both simple
high-level code and highly efficient compute kernels, thereby solving the
two-language problem --- at least to a significant extent. Highly efficient low-level
code will still look different from simple high-level code, but the
barrier between them is much smaller. In particular, this makes it easier for
users to transition to developers and contribute to a package. This also contributes
to the following observation:
